### 2016-07-17 FrontBackmatter/Publications.tex
Adjusted inclusion of papers.

%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[1]{Publications}{publications}
\chapter*{Publications}%\graffito{This is just an early --~and currently ugly~-- test!}

@@

%\noindent Put your publications from the thesis here. The packages
%\texttt{multibib} or \texttt{bibtopic} etc. can be used to handle
%multiple different bibliographies in your document.

\begin{refsection}[ownpubs]
    \nocite{*} % is local to to the enclosing refsection
    \printbibliography[env=nolabelbib, notcategory=cited, heading=none]
\end{refsection}

>>>>

%*******************************************************
% Publications
%*******************************************************
\thispagestyle{empty}
\refstepcounter{dummy}
\pdfbookmark[1]{Publications}{Publications}
\chapter*{Publications}%\graffito{This is just an early --~and currently ugly~-- test!}

@@

\begin{enumerate}[label=\textbf{\Roman{*} },ref=\Roman{*}]

\item
  \textbf{R. Di Remigio}, R. Bast, L. Frediani, and T. Saue:
  "Four-Component Relativistic Calculations in Solution with the
  Polarizable Continuum Model of Solvation: Theory,
  Implementation, and Application to the Group 16 Dihydrides
  \ce{H2X} (\ce{X} = \ce{O}, \ce{S}, \ce{Se}, \ce{Te},
  \ce{Po})",
\textit{J. Phys. Chem. A}, \textrm{2015}, \textbf{119}, 5061--5077
\label{relapcm}

\item
  M. Bugeanu, \textbf{R. Di Remigio}, K. Mozgawa, S. S. Reine, H.
  Harbrecht,  and L. Frediani:
  "Wavelet Formulation of the Polarizable Continuum Model. II. Use of
  Piecewise Bilinear Boundary Elements",
  \textit{Phys. Chem. Chem. Phys.}, \textrm{2015}, \textbf{17},
  31566--31581
\label{wemlin}

\item \textbf{R. Di Remigio}, K. Mozgawa, H. Cao, V. Weijo, and L.
  Frediani:
  "A Polarizable Continuum Model for Molecules at Spherical
  Diffuse Interfaces",
  \textit{J. Chem. Phys.}, \textrm{2016}, \textbf{144}, 124103
\label{spherical}

\end{enumerate}
